Clique and Constraint Models for Maximum Common (Connected) Subgraph Problems

### 2016-03-15 paper/paper.tex
An algorithm
More graphs and data

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-plain}
    \caption{Clique versus CP, connected, undirected, unlabelled, up to 25 vertices (and some 30 and
        35, which are still running\ldots). On the top, the cumulative number of instances solved by
    each approach, in under a certain time. On the bottom, the best clique approach compared to the
best CP approach: the colour at a point indicates the number of instances with these runtimes.}
\label{figure:connected-plain}
\end{figure}

>>>>

\begin{algorithm}[tb] \DontPrintSemicolon
\nl $\FuncSty{cliquishMCCIS}$ :: (Graph $G_1$, Graph $G_2$) $\rightarrow$ Map \;
\nl \Begin{
    \nl $\KwSty{global} ~ C_{\mathit{max}} \gets \emptyset$ \;
    \nl $G \gets \FuncSty{encode}(G_1, G_2)$ \;
    \nl $\FuncSty{expand}(G, \operatorname{V}(G), \emptyset, \emptyset)$ \;
    \nl $\KwSty{return} ~ \FuncSty{decode}(C_{\mathit{max}})$ \;
}
\vspace{1ex}
\nl $\FuncSty{expand}$ :: (Graph $G$, Set $C$, Set $A$, Set $P$) \;
\nl \Begin{
    \nl $\mathit{colourClasses} \gets \FuncSty{colour}(G, A, P)$ \;
    \nl \While{$\FuncSty{length}(\mathit{colourClasses}) > 0$}{
        \nl \ForEach{$v \textnormal{~in~} \FuncSty{last}(\mathit{colourClasses}) \textnormal{~in reverse order}$}{
            \nl \lIf{$|C| + \FuncSty{length}(\mathit{colourClasses}) \leq |C_{\mathit{max}}|$}{\KwSty{return}}
            \nl \lIf{$v \notin A ~ \KwSty{and} ~ C \ne \emptyset$}{\KwSty{return}}
            \nl $C' \gets C \cup \{ v \}$\;
            \nl \lIf{$|C'| > |C_{\mathit{max}}|$}{$C_{\mathit{max}} \gets C'$}
            \nl $A' \gets A \cup \FuncSty{connected}(v)$ \;
            \nl $P' \gets P \cap \operatorname{N}(G, v)$ \;
            \nl \lIf{$P' \neq \emptyset$}{$\FuncSty{expand}(G, C', A', P')$}
         }
         \nl $\FuncSty{removeLast}(\mathit{colourClasses})$ \;
     }
}
\vspace{1ex}
\nl $\FuncSty{colour}$ :: (Graph $G$, Set $A$, Set $P$) $\rightarrow$ List of List of Vertex \;
\nl \Begin{
    \nl $\KwSty{return}$ a greedy colouring of $P \setminus A$, followed by a greedy colouring of $P
    \cap A$, both using static degree order in $G$ \;
}
\caption{A clique-inspired algorithm for MCCIS.}
\label{algorithm:mc}
\end{algorithm}

@@

\begin{figure}[p]
    \centering
    \input{gen-graph-connected-plain}
    \caption{Clique versus CP, connected, undirected, unlabelled, up to 35 vertices. On the top, the
    cumulative number of instances solved by each approach, in under a certain time. On the bottom,
    the best clique approach compared to the best CP approach: the colour at a point indicates the
    number of instances with these runtimes.}
\label{figure:connected-plain}
\end{figure}
